A Hitchhiker's Guide to Reproducible Research in R

### 2021-07-30 manuscript.Rmd
the pdf version is the actual dependency
rename second section

    - images/nutshell.svg

@@

This tutorial therefore demonstrates how to make R-based research projects reproducible, while striking a balance between rigor and ease-of-use.
A rigorous standard increases the likelihood that a project will remain reproducible as long as possible.
An easy-to-use standard, on the other hand, is more likely to be adopted.
Our approach is to promote broad adoption of easy-to-use practices, i.e., a "low threshold", and ensure that these practices are compatible with more complex rigorous solutions, i.e., a "high ceiling".
As researchers become more proficient with the tools involved, they can thus improve the reproducibility of their work.
The first part of this tutorial outlines a reproducibility standard, and introduces the underlying theoretical concepts and software solutions.
The second part is a tutorial that demonstrates how this standard can be easily adopted with the help of the R package `repro`.

@@

# Concepts and Software Solutions<!--CJ Some inconsistencies:
1) From the end of the previous paragraph, I would expect a description of the "rigorous reproducibility standard" here.
2) The paragraph is labeled "Concepts and Software SOlutions, but it begins with a list of threats to reproducibility. Threats are not concepts nor software solutions.
3) After the list of threats, we get a description of the "rigorous reproducibility standard". That is what I would expect based on the preceding paragraph. Note that the "rigorous reproducibility standard" is also not a concept, nor a software solution. Consider re-naming this section.-->

From our own experience with various research projects, we identified the following common threats to reproducibility: <!-- CJ This still requires attention! How did you identify these causes? Is this exhaustive?-->

>>>>

    - images/nutshell.pdf

@@

This tutorial therefore demonstrates how to make R-based research projects reproducible, while striking a balance between rigor and ease-of-use.
A rigorous standard increases the likelihood that a project will remain reproducible as long as possible.
An easy-to-use standard, on the other hand, is more likely to be adopted.
Our approach is to promote broad adoption of easy-to-use practices, i.e., a "low threshold", and ensure that these practices are compatible with more complex rigorous solutions, i.e., a "high ceiling".
As researchers become more proficient with the tools involved, they can thus improve the reproducibility of their work.
The first part of this tutorial outlines threats to reproducibility and how the here presented reproducibility standard addresses these threats.
The second part is a tutorial that demonstrates how this standard can be easily adopted with the help of the R package `repro`.

@@

# Threats to reproducibility and appropriate remedies

From our own experience with various research projects, we identified the following common threats to reproducibility:
